---
title: "Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette compiles a variety of examples, most taken straight from [Stack Overflow](https://stackoverflow.com/). When possible, I will link the source of the example. To run any of the examples (i.e. copy/paste), load the following package:

```{r setup, message=FALSE}
library(RVerbalExpressions)
```

## Extract all words after a specific tag

In this example, we want to extract every word that comes after a @, including the @. To do this, we will:

```{r}
string <- "nowy commit, nowa przygoda @OSKI @data2 @pankote testujemy kod @oski2"

x <- rx() %>% 
  rx_find("@") %>% 
  rx_alphanum() %>% 
  rx_one_or_more()

# base R approach
unlist(regmatches(string, gregexpr(x, string)))

# stringr approach
# stringr::str_extract_all(string, x)
```

1. First, construct the verbal expression with `rx`
2. Then, `rx_find` the @ tag
3. Then, match all alphanumeric characters
4. Then, match `one_or_more` characters in the range

Source: https://stackoverflow.com/questions/31105862
